Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-06 paper/paper.tex
Update parameter count

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions scraped from online
newspapers. To the best of our knowledge, all existing models that are trained
on these news datasets use template-based methods to insert named entities.

@@

Recent image captioning systems are based mostly on ``Show, Attend, Tell"
\cite{Xu2015ShowAA}, which uses a simple hard attention over the image. Later
improvements include giving the model the option to not attend to any image
region \cite{Lu2017KnowingWT}, using reinforcement learning to directly
optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and using a
bottom-up approach to propose a region to attend to
\cite{Anderson2017BottomUpAT}. All of these systems generate generic captions.

A more challenging task is to generate captions for news images, in which we
need to be able to generate entity names. There are non-neural approaches
\cite{Feng2013AutomaticCG,Tariq2017ACE}. Neural approaches include using the
word2vec representation of the article and and the VGG19 representation of the
image as context to the LSTM generator \cite{Ramisa2016BreakingNewsAA}.

@@

As a starting point, we use the GoodNews dataset, previously the largest
dataset on news image captioning. As part of the quality check, we also
reconstruct the same dataset on our own. We use the New York Times API and
write a custom parser to recollect and extract all the articles and images in
in the same period as GoodNews from the original source. We call this
GoodNews+. We managed to crawl all the original articles, but the number of
images is slightly less, either due to dead links or not crawling images
unrelated to the main article. GoodNews+ allows us to make the following
observations about the original GoodNews dataset:

@@

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
      \midrule
      GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\
      RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
      Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
      Transformer (location-aware) & 19.0 & 11.7 & 7.76 & 5.48 & 21.1 & 9.51 & 51.4 \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

@@

\begin{table*}[t]
	\caption {Model complexity: Number of trainable parameters}
	\label{tab:models}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Parameters \\
      \midrule
      GloVe + LSTM & 153M \\
      GloVe + Transformer & 148M \\
      RoBERTa + LSTM & 139M \\
      RoBERTa + Transformer & 154M \\
        + faces & 171M \\
        + names & 175M \\
        + faces + names & 192M \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions written by professional
journalists. To the best of our knowledge, all existing models that are trained
on these news datasets use template-based methods to insert named entities.

@@

Recent image captioning systems are based mostly on ``Show, Attend, Tell"
\cite{Xu2015ShowAA}, which uses a simple hard attention over the image. Later
improvements include giving the model the option to not attend to any image
region \cite{Lu2017KnowingWT}, using reinforcement learning to directly
optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and using a
bottom-up approach to propose a region to attend to
\cite{Anderson2017BottomUpAT}. All of these systems can only generate generic
captions with a limited vocabulary.

A more challenging task is to produce captions for news images, in which we
need to be able to generate entity names. There are non-neural approaches
\cite{Feng2013AutomaticCG,Tariq2017ACE}. Neural approaches include using the
word2vec representation of the article and and the VGG19 representation of the
image as context to the LSTM generator \cite{Ramisa2016BreakingNewsAA}.

@@

As a starting point, we use the GoodNews dataset, previously the largest
dataset on news image captioning. As part of the quality check, we also
reconstruct the same dataset on our own. We use the New York Times API and
write a custom parser to recollect and extract all the articles and images in
the same period as GoodNews from the original source. We call this GoodNews+.
We were able to crawl all the original articles, but the number of images is
slightly less, either due to dead links or not crawling images unrelated to the
main article. GoodNews+ allows us to make the following observations about the
original GoodNews dataset:

@@

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
      \midrule
      GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
      RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
      Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
      Transformer (location-aware) & 19.0 & 11.7 & 7.76 & 5.48 & 21.1 & 9.51 & 51.4 \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

@@

\begin{table*}[t]
	\caption {Model complexity: Number of trainable parameters}
	\label{tab:models}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Parameters \\
      \midrule
      GloVe + LSTM & 157M \\
      GloVe + Transformer & 148M \\
      RoBERTa + LSTM & 159M \\
      RoBERTa + Transformer & 154M \\
        + faces & 171M \\
      %   + names & 175M \\
      %   + faces + names & 192M \\
		\bottomrule
	\end{tabular}
\end{table*}
